---
title: "Wine"
author: "Nathania"
date: "June 2, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Introduction
The white wine dataset contains a physicochemical properties and quality ratings.  Each wine sample comes with a quality rating from three to ten, and results from several physical chemical tests, such as: alcohol content, acidity level and residual sugar, etc. There are 11 columns describing their chemical properties, and a column for quality ratings.The objectives to build a predict the quality of the wine.

##### Description of features:

1 - fixed acidity: most acids involved with wine or fixed or nonvolatile (do not evaporate readily)

2 - volatile acidity: the amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste

3 - citric acid: found in small quantities, citric acid can add 'freshness' and flavor to wines

4 - residual sugar: the amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with greater than 45 grams/liter are considered sweet

5 - chlorides: the amount of salt in the wine

6 - free sulfur dioxide: the free form of SO2 exists in equilibrium between molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial growth and the oxidation of wine

7 - total sulfur dioxide: amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine

8 - density: the density of water is close to that of water depending on the percent alcohol and sugar content

9 - pH: describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale

10 - sulphates: a wine additive which can contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial and antioxidant

11 - alcohol: the percent alcohol content of the wine

Output va (based on sensory data):

12 - quality (score between 3 and 9)

The objectives is to discover which of these chemical propeties influence the quality of wine and to understand how these characteristics influence the quality.At the end, we will create a model to predict the quality of wine.

```{r}
library(ggplot2)
library(gridExtra)
library(grid)
library(dplyr)
library(reshape2)
library(GGally)
library(scales)
library(ggpubr)
library(memisc)
library(caret)
library(tidyverse)
```

```{r}

fileName <- 'winequality-white.csv';
if (!file.exists(fileName)) {
  download.file(paste0('https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/', fileName), fileName, method="curl")
}

```

Take a look of the data
```{r}
df <- read.csv('winequality-white.csv', sep=';')
glimpse(df)
```
### Data Cleaning
We'll check missing values,as well as the duplicated values.
```{r}
#Check missing values
sum(is.na.data.frame(df))

#Check duplicated values 
sum(duplicated(df))
```

Now we have no duplicated values
```{r}
#filter any duplicated rows
df <- df %>% distinct()
#confirm there are no duplicated rows
sum(duplicated(df))

```
Let's summarize the data, notice here the quality of wine lies between 3 and 9
```{r}
summary(df)
```
### Data Exploratory

The target va is Quality therefore it's important to know it's distribution, let's look at the distribution of the wine's quality.
```{r}
ggplot(aes(quality), data = df) +
  geom_bar(color = "black", fill = "salmon")

table(df$quality)
```

Most wine samples are of 5 and 6 (almost 80% of the dataset). Moreover, it seems to be that wines which received the highest score (9) have a few observations, and this situation repeats in the lowest level( 3, 4). Wines with a score of 7 are 855 observations. Then, I will compare the median and mean of physicochemical properties for the 3, 5, 6, 9 quality levels to understand the main differences among them.

```{r}
#exclude (droping) index of the dataset
col <- names(df) %in% "X"
winequality <- df[!col]

# Create a function to compare the mean and median between highest, average and lowest 
# scores of all vas
mean_median <- function(func.) {
# this va creates a new data frame by selecting only rows with quality equal 3
q3 <- data.frame(summarize_all(subset(winequality, quality == 3),
                                      .funs= func.))
    
# this va will creates a new data frame by selecting only rows with quality equal 
# 5 or 6
q56 <- data.frame(summarize_all(subset(winequality, quality == 5 | 
                                      quality == 6), .funs= func.))
                                      
# this va will creates a new data frame by selecting only rows with quality equal 9
q9 <- data.frame(summarize_all(subset(winequality, quality == 9),
                                      .funs= func.))

# this va joins our three new data frames (q3, q56, q9) vertically. 
comb <- rbind(q3, q56, q9)

# convert quality colunm in integer number
comb$quality = as.integer(comb$quality)

# reorder the columns in our new dataframe
comb [, c(12, 1:11) ]
}

head(df)

```

```{r}
#Check the mean of all vas based on highest, average and lowest score.
mean_median(mean)
```

There are significant variations of mean and median with sulfur dioxide (free and total sulfur) and acidity (fixed, volatile and citric) vas and residual sugar. In order to avoid problems with outliers, we will consider only the median.

Notice that wine with highest score, i.e. 9 have the lowest level of density, sulfur dioxide and sugar (the lowest score has the same median). Furthermore, they have highest level of alcohol, citric acid, and pH.

Summarizing above, we can see that:
  - What attributes increase values with a better rating? 
      Alcohol, citric acid, pH
  - What attributes decrease values with a better rating?
      density, sulfur dioxide and sugar 



```{r}
# The objective of this function is to create charts to analyze the distribution and outliers of features

# wine distribution
wdist <- function(va, varName = '', bins = 30) {

#Print charts with outliers
## Building a Histogram:
his <- ggplot(data = df) +
    geom_histogram(aes(x = va), bins = bins,
                   fill = 'brown', colour='black') +
    labs(x = varName)

## histogram with scale log10
hislog10 <- his + scale_x_log10() + 
    labs(x = paste('log10(', varName,')'))

## Building a boxplot:
bxplot <- ggplot(df, aes(x = 1, y = va)) + 
    geom_boxplot(color = 'black', fill = 'brown') + 
    labs(x ='count', y = varName) + 
  coord_flip()

## Building density plot
dsplot <- ggplot(aes(x = va, 
                           y = ..count../sum(..count..)), data = df ) +
geom_density(fill = 'brown', binwidth = 10) +
scale_x_continuous() +
 labs(x = varName, y = 'count')

## Arranging all the plots:
ggarrange(his, hislog10, dsplot, bxplot,  nrow = 4)               
        
}

```

##### Fixed Acidity
```{r}
wdist(df$fixed.acidity, 
        varName = 'Fixed Acidity (tartaric acid - g / dm^3)')

```
There are two things to notice:
Distribution: Right-skewed, there is a long tail.
Outliers: The boxplot shows a few outliers from 8 to 16.

##### Volatile Acidity
```{r}
wdist(df$volatile.acidity, 
        varName = 'Volatile Acidity (acetic acid - g / dm^3)')

```

Distribution: The first histogram appears bimodal with peaks around 0.27, but when we zoom into the histogram with log10, it seems there's right-skewed distribution. Further, there is a long tail.
Outliers: There are a few outliers between the higher range, around 0.5 to 12.0


#####  Citric Acid
```{r}
wdist(df$citric.acid ,
        varName = 'Citric Acid (Citric Acid - g / dm^3)')

```
Distribution: The first histogram appears right-skewed with high peak around 0.30 and with a short tail. When we use the histogram with log10, it seems to be the distribution changes the direction to the left and creates a long tail.

Outliers: There is There are a few outliers between the higher range, around 0.6 to 1.7

#### Sugar
```{r}
wdist(df$residual.sugar ,
        varName = 'Sugar (Residual Sugar - g / dm^3)')
```
It's hard to clearly see the distribution of sugar because of the long tail, we will create new a histogram with breaks and limits.

```{r}
ggplot(data = df) +
    geom_histogram(aes(x = residual.sugar),
                   fill = 'salmon', colour='black') +
  scale_x_continuous(breaks = seq(1, 4, 0.25), 
                     limits = c(1, 4)) +
    labs(x = "Residual Sugar")

```

Distribution: It has a right-skewed distribution with a long tail (from 20 to 65). The distribution with log10 appears right-skewed with a long tail to the right.

Outliers: There are many outliers with a large range (from 20 to 65).

#### Chlorides
```{r}
wdist(df$chlorides,
        varName = 'Chlorides (g / dm^3)')

```
Again, we will create a new histogram with breaks and limits.

```{r}
ggplot(data = df) +
    geom_histogram(aes(x = chlorides),
                   fill = 'salmon', colour='black') +
  scale_x_continuous(breaks = seq(0, 0.15, 0.020), 
                     limits = c(0.03, 0.14)) +
    labs(x = "Chlorides")

```

Distribution: It has right-skewerd distribution with a long tail (from 0.06 to 0.35). The distribution with log10 appears symmetrical with a long tail to the right. Aftedfards, adjusting the distribution continues to be symmetrical.

Outliers: There are many upper outliers with an extensitve range (around 0.06 and 0.35) and a few lower outliers (around 0.1 and 0.2).

#### Free Sulfur Dioxide

```{r}
wdist(df$free.sulfur.dioxide,
        varName = 'Free Sulfur Dioxide (g / dm^3)')


```
Distribution: The first histogram appears right-skewed, but when we zoom into the histogram with log10, it seems to be bimodal with peaks around 25 and 30. Further, there is also a short tail.

Outliers: There are a few outliers with a range around 80 to 140.

#### Total Sulfur Dioxide
```{r}
wdist(df$total.sulfur.dioxide,
        varName = 'Total Sulfur Dioxide (g / dm^3)')

```
Distribution: The first histogram appears right-skewed, but when we zoom into the histogram with log10, change direction to left-skewed. Furthermore, there is a long tail.

Outliers: There are many outliers with a higher range, around 260 to 430.


#### Density
```{r}
wdist(df$density,
        varName = 'Density (g / dm^3)')

```
Distribution: The distribution of density is left-skewed for all plots.

Outliers: There is outliers with higher range, around 1.025 and 1.028.

#### pH
```{r}
wdist(df$pH,
        varName = 'pH (g / dm^3)')
```
Distribution: The distribution of density is symmetrical for all plots.

Outliers: There is outliers which lies in 3.6 to 4.3

#### Sulphates
```{r}
wdist(df$sulphates,
        varName = 'Sulphates (g / dm^3)')
```
Distribution: It left-skewed, as we zoomed into log10, it change to right-skewed. It also has a long tail.

Outliers: There are many outliers with a higher range, around 0.77 to 1.4.


#### Alcohol
```{r}
wdist(df$alcohol,
        varName = 'Alcohol (g / dm^3)')
```
Distribution: It seems almost a symmetrical distribution but instead it has a short tail.

Outliers: There are a no outlier.

### Correlation Analysis
```{r}
#Investigate the relationship between all vas with correlation matrix 

# Building Correlation Matrix with all vas
library(corrplot)
#wq is data frame without index that was created in line 109
# ggcorr will use spearman method in all observations to plot a correlation matrix
ggcorr(winequality, 
       method = c("all.obs","spearman"),
       nbreaks = 4, palette = 'RdBu', label = TRUE, 
       name = "spearman correlation coeff.(rho)",
       hjust = 0.8, angle = -30, size = 3) +
  ggtitle("Spearman Correlation coefficient Matrix")


```
Positive correlation between:
- Quality - Alcohol : 0.5
- Density - Sugar: 0.7
- Density- Chlorides: 0.5
- Density - Total Sulfur Dioxide: 0.6
- Total Sulfur Dioxide - Free Sulfur Dioxide: 0.6
Negative correlation between:
- Quality - Volatile Acid: -0.4
- Density - Alcohol : -0.8
- pH - Fixed Acid: -0.4
- pH - Citric Acid: -0.2
- pH -Sugar: -0.2
- Citric Acid - Volatile Acid: -0.2

#### Correlation Network
```{r}
library(ggcorrplot)
#Investigate the relationship between all vas with network analysis
correlations <- cor(as.matrix(df))
threshold <- 0.6
cc0 <- correlations
diag(cc0) <- 0
ok <- apply(abs(cc0) >= threshold, 1, any)
correlations <- correlations[ok, ok]
correlations <- as.data.frame(correlations)

ggcorrplot(correlations, hc.order = TRUE, type = "lower",
           lab = TRUE)
```

#### Bivariate Analysis
```{r}

#Bulding function to analyze categorical va and continuos va
w_bxplot <- function (va1, varName = '',
                        va2, varName1 = '') {
  
  boxplot <- ggplot(aes(x = factor(va1), y = va2), 
                    data = df) +
  geom_boxplot(color = 'black', fill = "lightblue") +
    labs(x = varName, y = varName1)
  plot(boxplot)
}


library(ggpubr)
#Bulding function to analyze continuos vas
w_scplot <- function(varName = '', varName1 = '', 
                       varName2 = '', varName3 = '' ) {
                       

  #Building scatter plot 
  scatter <- ggscatter(df, x = varName, y = varName1,
              conf.int = TRUE, color = "orange",
              fill = "orange", cor.coef = TRUE, 
              cor.method = "pearson") +
    theme_dark() +
    labs(title = paste(varName2, "vs", varName3, "scatter plot"))
  
  # Building scatter plot and add a linear regression line
  scatter2 <- ggscatter(df, x = varName, y = varName1,
              add = "reg.line", conf.int = TRUE, color = "orange", 
              add.params = list(color = "grey20"), cor.coef = TRUE, 
              cor.method = "pearson", alpha = 0.3) +
    theme_dark() +
    labs(title = paste(varName2, "vs", varName3, 
                       "scatter plot with linear regression"))
  
  # Building scatter plot and add a fiting regression line
  scatter3 <- ggscatter(df, x = varName, y = varName1,
              add = "loess", conf.int = TRUE, color = "orange",
              add.params = list(color = "grey20"), cor.coef = TRUE,
              cor.method = "pearson", alpha = 0.3) +
    theme_dark() +
    labs(title = paste(varName2, "vs", varName3, 
                       "scatter plot with fiting regression"))
  
  ggarrange(scatter, scatter2, scatter3,  nrow = 3)
}
```

###### Quality vs Alcohol
```{r}
w_bxplot(df$quality, varName = 'Quality', df$alcohol, 
           varName1 = 'Alcohol')
by(df$alcohol, df$quality, summary)
```

The trend between alcohol and quality is clearer,the amount of alcohol increases with better quality ranking. Additionally, most outliers have a score of 5, and that explains why the median is lower than score of 4.

##### Quality vs Volatile Acidity
```{r}
w_bxplot(df$quality, varName = 'Quality', df$volatile.acidity, 
           varName1 = 'Volatile Acid')
by(df$quality, df$volatile.acidity, summary)


```
Volatile acidity shows an opposite trend, the worst score quality having the largest median. By way of explanation, the amount of volatile acidity decreases with a better quality ranking.



##### Density vs Alcohol scatter plot
```{r}
w_scplot(varName = "density", varName1 = "alcohol", 
           varName2 = "Density", varName3 = "Alcohol")
```

There is a moderate negative correlation between density vs alcohol. That means when the level of alcohol decreases, the density increases. We can see this pattern with the line models.

##### Density vs Sugar scatter plot
```{r}
w_scplot(varName = "density", varName1 = "residual.sugar", 
           varName2 = "Density", varName3 = "Residual Sugar")
```
There is a weak positive correlation between density and sugar . That means the level of fixed acidity increases as the density increases. We can see this trend with the line models.


##### Density vs Fixed.acidity scatter plot
```{r}
w_scplot(varName = "density", varName1 = "fixed.acidity", 
           varName2 = "Density", varName3 = "Fixed Acidity")
```
There is a weak positive correlation between density and fixed acidity. We can see with the line model a slight increased trend. So, as the fixed acidity rises, the density grows slightly.

##### Volatile vs Citric Acid scatter plot
```{r}
w_scplot(varName = "volatile.acidity", varName1 = "citric.acid", 
           varName2 = "Volatile Acidity", varName3 = "Citric Acid")

```

Volatite acidity and citric acid have a moderate negative correlation, almost zero correlation. It seems they don't have relationship to each other.

#### Bivariate Analysis Summary
Since quality is a categorical ordinal va, we analyzed it vs continuous va with a box plot. Then, we examined continuous vas between each other with a scatter plot. We further applied a regression line that allows us to understand the pattern between these correlations.

The box plots show how alcohol and volatile acidity influence the quality rating. In others words, the quality va has only a moderate positive correlation with alcohol (0.5), and a moderate negative correlation with volatile acidity (-0.4). Quality does not have other moderate or strong correlations.

In addition, we saw how alcohol, sugar, and chlorides affect the va density. Density has a strong negative correlation with alcohol (-0.5), and a strong positive correlation with residual sugar, The sulfur dioxide. The pH va has a strong negative correlation with fixed acid and moderate negative correlation with citric acidity and Sugar.

#### Multivariate Analysis
```{r}
# use function "factor" to enconde "quality" as factor with default order
df$quality = factor(df$quality)


# building function with scatterplot colored by quality
multi_ <- function(va, varName = '', va1, varName1 ='') {

    ggplot(df, aes(x = va, y = va1, color = quality)) +
    geom_jitter() +
    # color enconding
    scale_color_brewer(type = 'div', palette = "Blues") +
    # darken the background in order to see light colored points
    theme_dark() + 
    labs(x = varName, 
         y = varName1, 
         title = paste("Scatterplot between", varName, "and", 
           varName1 = '', "with colored quality rating"))

}

#Building function to facet the scatterplot by quality score with regression
multi_2 <- function(varName = '', varName1 = '', varName2 = '', 
                       varName3 = '' ) {

  s2 <- ggscatter(df, x = varName, y = varName1, facet.by = "quality",
            add = "reg.line", add.params = list(color = "grey20"), 
          conf.int = TRUE, color = "lightblue", fill = "grey", 
            cor.coef = TRUE, cor.method = "pearson", alpha = 0.5) +
    theme_dark() +
    labs(title = paste(varName2, "vs", varName3, 
                       "scatter plot with linear regression"))

  s3 <- ggscatter(df, x = varName, y = varName1, facet.by = "quality",
              add = "loess", add.params = list(color = "grey20"), 
            conf.int = TRUE, color = "lightblue", fill = "grey", 
              cor.coef = TRUE, cor.method = "pearson", alpha = 0.5) +
    theme_dark() +
    labs(title = paste(varName2, "vs", varName3, 
                       "scatter plot with fiting regression"))

ggarrange(s2, s3, nrow = 2)

}

```

##### Density VS Alcohol
```{r}
multi_(df$density, varName = 'Density (g/cm³)', df$alcohol, 
       varName1 = 'Alcohol (% by volume)')


```
 Most of the samples with a 7 and 8 quality score appear above 10% of alcohol and below 0.995 of density. Wines with a low score are distributed around 9% to 10% of alcohol and a density concentration of about 0.995 to 1.000.

```{r}
multi_2(varName = "density", varName1 = "alcohol", 
        varName2 = "Density", varName3 = "Alcohol")
```
Comparing density VS alcohol by quality, we can see a strong negative correlation between density and alcohol by quality scores, except a score of 9. The samples with a score of 9 show the most strong negative correlation, i.e. 0.97.

##### Density vs Sugar
```{r}
multi_(df$density, varName = 'Density (g/cm³)', df$residual.sugar, 
       varName1 = 'Residual Sugar (g/dm³)')
```

Density and Sugar analyzed by quality show a strong positive linear correlation. We can see sugar increases as density increases.

```{r}
multi_2(varName = "density", varName1 = "residual.sugar", 
        varName2 = "Density", varName3 = "Sugar")
```

The density and sugar have a strong positive correlation when analyzed by quality, except for 9 it is the strongest.

##### Density vs Fixed acidity
```{r}
multi_(df$density, varName = 'Density (g/cm³)', df$fixed.acidity, 
       varName1 = 'Fixed Acidity (g/dm³)')

```
Density vs Fixed acidity analyzed by quality show a strong positive linear correlation. We can see fixed acidity increases as density increases.

```{r}
multi_2(varName = "density", varName1 = "fixed.acidity", 
        varName2 = "Density", varName3 = "Fixed Acidity")
```
When we compare density vs fixed acidity with regression, the plots show a linear trend, and all scores have a weak positive correlation with the highlight being a score of 9 that has a 0.98 correlation.

##### Density vs Citric Acid
```{r}
multi_(df$density, varName = 'Density (g/cm³)', df$citric.acid, 
       varName1 = 'Citric Acid (g/dm³)')

```
Density vs Fixed acidity analyzed by quality shows a weak positive correlation and most of the samples appear less than 0.5 of citric acid. Moreover, both quality scores seem to be distributed around 0.99 to 1.0 of citric acid.

```{r}
multi_2(varName = "density", varName1 = "citric.acid", 
        varName2 = "Density", varName3 = "Citric Acid")
```
Comparing density VS citric acid analyzed for each quality scores separately, we can see a weak positive correlation for all of them, except for 9 it has a moderate positive correlation.


##### Volatile vs Citric Acid
```{r}
multi_(df$volatile.acidity, varName = "Volatile Acidity (g/dm³)", 
       df$citric.acid, varName1 = "Citric Acid (g/dm³)")
```
It seems to be that most of the observations are distributed in volite acidity between 0.15 and 0.45. 

```{r}
multi_2(varName = "volatile.acidity", varName1 = "citric.acid", 
        varName2 = "Volatile Acidity", varName3 = "Citric Acid")
```
Volatile vs citric acid show a weak negative correlation, except for the highest quality score, which has a strong negative correlation, i.e. 0.69.

#### Multivariate Analysis Summary
There is a strong positive correlation between density vs fixed acidity, alcohol, and sugar, i.e. 0.98, 0.97 and 0.95 respectively.

For highest wine quality:
- There is a strong negative correlation between Volatile vs citric acid, i.e. 0.69
- There is a moderate positive correlation between density vs citric acid, i.e. 0.5
- There is a strong positive correlation between density and sugar, i.e. 0.95

#### Model

There are 4 algorithm which will be used and evaluated, such as Classification and Regression Trees (CART). k-Nearest Neighbors (kNN). Support Vector Machines (SVM) with a linear kernel. Random Forest (RF)

The range of wine quality is 3-9, which will divide into three levels, [high, medium, low]. The validation set is about 20% from the dataset. We'll perform 10 cross validation on validation set.

```{r}
#Classification model

#Use a copy of the original data set
wine <-read.csv('winequality-white.csv', sep=';')



wine$quality_levels <- cut(wine$quality, breaks = c(3, 4, 6, 9),
                            labels = c('low','medium', 'high')) 


# create a list of 80% of the rows in the original dataset we can use for training
validation_index <- createDataPartition(wine$quality_levels, 
                                        p = 0.80, list = FALSE)

# select 20% of the data for validation
validation <- wine[-validation_index,]

# use the remaining 80% of data to training and testing the models
wine1 <- wine[validation_index,]
str(wine)

```

```{r}
#Active packages
library(memisc)
library(RColorBrewer)
library(caret)
library(ggpubr)
library(magrittr)
```

```{r}
# Run algorithms using 10-fold cross validation
control <- trainControl(method ="cv", number = 10)
metric <- "Accuracy"
```


```{r}
# a) nonlinear algorithms

# CART
fit.cart <- train(quality_levels ~., data = wine, metric = metric, 
                  method="rpart", trControl = control, 
                  na.action=na.exclude) 
                  
# kNN
fit.knn <- train(quality_levels~., data = wine, metric = metric, 
                 method="knn", trControl = control, 
                 na.action = na.exclude)
                 

# b) advanced algorithms

# SVM
fit.svm <- train(quality_levels~., data = wine, method ="svmRadial", 
                 trControl = control, na.action = na.exclude)
# Random Forest
fit.rf <- train(quality_levels~., data = wine, method ="rf",  
                trControl=control, na.action = na.exclude)

```


##### Evaluate the Best Model
```{r}
# summarize accuracy of models
results <- resamples(list(cart = fit.cart, knn = fit.knn, 
                          svm = fit.svm, rf = fit.rf))
summary(results)
```
CART and RF models achieve 100% accuracy. Now, I will summarize both models to figure out which one is the best.

##### Summarize the Best Model
```{r}
# summarize Best Model
print(fit.cart)

print(fit.rf)

```
It seems that the random forest model was more accurate than the classification and regression trees model.

##### Generate Predictions
The RF was the most accurate model.Therefore, we'll apply it to the validation set, i.e. 20% from the wine dataset and used confusion matrix as metric evaluator.

```{r}
# estimate skill of RF on the validation dataset
predictions <- predict(fit.rf, validation)
confusionMatrix(predictions, validation$quality_levels)

dim(validation)
```
Our model gets 100% accuracy in the test with the validation set. It is important to remember that the validation only contains a small part (20%) of our original dataset. This explains why our accuracy was so high. We need to test this model in other wine data sets to evaluate if it is a reliably accurate mode

```{r}
predtb <- cbind.data.frame(predictions, validation$quality_levels)
colnames(predtb) <- c('predictions', 'actual')
predtb[1:30,]
```

### Conclusions
The white wine data set contains information on almost 4698 white wine samples across 12 chemical properties. Descriptive statistics using a histogram, histogram log10, density and box plots is used to find the distribution for each separated variable. Statistics computation was calculated such as mean, median, max, etc.  The mean was not totally reliable in a few attributes as sugar and chlorides. These attributes had a significant differenctrom the median, and this situation is common for outliers. Therefore, the median is used to gather the main characteristics for the quality levels. 

For highest wine quality:
  - High level of alcohol, citric acid, and pH.
  - Low level of density, sulfur dioxide and sugar.
  - Medium level of fixed acidity and volatile acidity
  

Correlation matrix, correlation network, boxplot, scatter plot and scatter plot with fitting regression were used to examine the correlation between these properties. 

The quality variable had a meaningful correlation with alcohol and volatile acidity. There is a positive trend between quality and alcohol, so the level of alcohol increases with a better quality ranking. The opposite occurs with quality and volatile acidity, and the level of volatile acidity decreases with a better quality ranking. This completely makes sense because high levels of volatile acidity lead to an unpleasant, vinegar taste. 

Besides that, we saw how alcohol and volatile acidity (the attributes correlated with quality) were influenced or influence other variables, such as density.

In the multivariate analysis, we analyzed alcohol vs density, volatile acidity vs citric acid and alcohol vs volatile acidity interpreted by quality with scatter plot and regression model. We found that there is a strong positive correlation between density vs fixed acidity, alcohol, and sugar, i.e. 0.98, 0.97 and 0.95 respectively. Weak positive correlation with citric acid and fixed acid. While there's a strong negative correlation between density and alcohol

Finally, four classification models to predict whether wine is high, medium or low quality. The best model was developed with random forest method, this model achieves 100% accuracy in our test with the validation data set. As our validation data set contains only 20% observations, but we strongly recommend testing this model in other wine data sets to evaluate if it is a reliable model.
